The sweet spot for local polygenic adaptation: a case study motivated by stickleback

### 2018-08-22 Stickleback_Paper.tex
little edits

As the number of common, locally adaptive alleles decreases,
the genetic basis of adaptation is more commonly shared.
Figure \ref{fig:MPFAI}B shows
the distribution of the mean percentage of currently-defined freshwater adapted alleles 
that each genome in each of the populations carries,
averaged across time and individuals.
If all individuals across lakes carried the same set of alleles determining their trait value,
this would be 100\%.
This value is nearly reached at the highest migration rate;
but it is lower due to migration load.
At the lowest migration rate, 
each genome in the original lakes have almost exactly $1/25^{th} = 0.04\%$   
of the total freshwater adapted alleles --
since there are 25 lakes, this implies that each lake has adapted with a unique set of alleles.
Since these are \emph{pre-existing} alleles, the value is zero for introduced lakes.

In Figure \ref{fig:MPFAI}C we can see that; as migration rates increase, the number of these alleles decreases steadily.
On the left in Figure \ref{fig:MPFAI}B, we see the mean percentage of alleles per individual rapidly increases. 
Together, these two results strongly suggest the sharing genetic basis.
\jgg{TODO, reference the number of lakes that each allele appears in, make plot for supp}
%As a first indication of this, Figure \ref{fig:MPFAI}B shows that the introduced 
%population utilizes a higher percentage of "pre-existing freshwater adapted alleles"
%with higher rates of introgression between the populations.
Figure \ref{fig:MPFAI}A shows the distribution of the mean number of pre-existing freshwater adapted alleles,
Throughout the simulations, in each deme.
Interestingly, the genetic basis of the freshwater phenotype 
seems to simplify with greater $m$. 
This would seem to suggest higher rates of migration allowed 
adaptive alleles of higher effect to travel more efficiently through the populations
\jgg{is this right?}

>>>>

As the number of common, locally adaptive alleles decreases,
the genetic basis of adaptation is more commonly shared.
Figure \ref{fig:MPFAI}B shows
the percentage of currently-defined, freshwater-adapted alleles 
that each genome in each of the populations carries,
averaged across time and individuals.
If all individuals across lakes carried the same set of alleles determining their trait value,
this would be 100\%.
This value is nearly reached at the highest migration rate;
but it is lower due to migration load.
At the lowest migration rate, 
each genome in the original lakes have almost exactly $1/25^{th} = 0.04\%$   
of the total freshwater adapted alleles --
since there are 25 lakes, this implies that each lake has adapted with a unique set of alleles.
Since these are \emph{pre-existing} alleles, the value is zero for introduced lakes.

In Figure \ref{fig:MPFAI}C we can see that; as migration rates increase, the number of these alleles decreases steadily.
On the left in Figure \ref{fig:MPFAI}B, the mean percentage of alleles per individual rapidly increases. 
Together, these two results strongly suggest the sharing genetic basis.
\jgg{TODO, reference the number of lakes that each allele appears in, make plot for supp}
%As a first indication of this, Figure \ref{fig:MPFAI}B shows that the introduced 
%population utilizes a higher percentage of "pre-existing freshwater adapted alleles"
%with higher rates of introgression between the populations.
Figure \ref{fig:MPFAI}A shows the distribution of the mean number of pre-existing freshwater adapted alleles,
Throughout the simulations, in each deme.
Interestingly, the genetic basis of the freshwater phenotype 
seems to simplify with greater $m$. 
This would seem to suggest higher rates of migration allowed 
adaptive alleles of higher effect to travel more efficiently through the populations
\jgg{is this right?}
